%-------------------------
% CV in LaTeX
% Author: Youhyun Sung
% Based on a resume-style one-page layout adapted for pdflatex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.30}
\definecolor{text-grey}{gray}{0.08}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{12pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlist[itemize]{leftmargin=1.2em, itemsep=2pt, topsep=2pt}

\titleformat{\section}
  {\bfseries \vspace{2pt} \raggedright \large}
  {}{0em}{}[\color{light-grey}{\titlerule[1.5pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey}\small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

\begin{center}
  \textbf{\Huge Youhyun Sung} \\ \vspace{5pt}
  \small
  Seoul, South Korea \hspace{4pt} | \hspace{4pt}
  \href{mailto:youhyun8808@gmail.com}{youhyun8808@gmail.com} \hspace{4pt} | \hspace{4pt}
  \href{https://youhyun-sung.github.io}{youhyun-sung.github.io} \hspace{4pt} | \hspace{4pt}
  \href{https://github.com/youhyunsung}{github.com/youhyunsung} \\
  \vspace{-3pt}
\end{center}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Seoul National University}{2022 -- 2026}
    {M.A. in Aesthetics}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Graduate study in aesthetics, art theory, and visual perception.}
  \resumeItemListEnd

  \resumeSubheading
    {Hanyang University}{2015 -- 2021}
    {B.A. in German Language \& Literature}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Entered with honors and graduated with honors.}
  \resumeItemListEnd

  \resumeSubheading
    {University of Stuttgart}{2018 -- 2019}
    {Exchange Student}{Stuttgart, Germany}
  \resumeItemListStart
    \resumeItem{Completed exchange study supported by the Baden-Wurttemberg Stipendium.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Research Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Cognitive Systems Lab, Korea University}{Nov. 2025 -- Present}
    {Research Assistant}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Working under Prof. Christian Wallraven on empirical aesthetics and visual perception.}
    \resumeItem{Projects include ECVP work on valuation responses to Op Art and matched optical illusions.}
    \resumeItem{Contributing to VSAC research on fixation-dependent spatial perception in reversible Op Art images.}
    \resumeItem{Supporting manuscripts currently in preparation for \textit{i-Perception} and \textit{Perception}.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Work Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Frieze Seoul}{2023 -- 2024}
    {Freelancer}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Supported event operations in an international contemporary art fair environment.}
  \resumeItemListEnd

  \resumeSubheading
    {10th World Congress of Constitutional Law}{Feb. 2018 -- Jun. 2018}
    {Part-time Operation \& Planning Staff, Sungkyunkwan University}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Assisted program operations and planning for an international academic conference.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Teaching \& Service}
\resumeSubHeadingListStart
  \resumeSubheading
    {Homo Aestheticus Seminar}{2026}
    {Organizer}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Organized a seminar featuring visiting professor Claus-Christian Carbon.}
  \resumeItemListEnd

  \resumeSubheading
    {Seoul National University}{2025}
    {Teaching Assistant, Art and Science}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Supported course delivery and instruction across one academic year.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Scholarships}
\resumeSubHeadingListStart
  \resumeSubheading
    {Seoul National University Mentoring Scholarship}{2022 -- 2023}
    {Recipient}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Awarded mentoring scholarship during graduate study.}
  \resumeItemListEnd

  \resumeSubheading
    {Baden-Wurttemberg Stipendium}{2018 -- 2019}
    {Recipient}{Germany}
  \resumeItemListStart
    \resumeItem{Scholarship support of approximately EUR 7,000 for exchange study at the University of Stuttgart.}
  \resumeItemListEnd

  \resumeSubheading
    {Academic Excellence Scholarship, Hanyang University}{2016 -- 2017}
    {Recipient}{Seoul, South Korea}
  \resumeItemListStart
    \resumeItem{Received merit-based academic scholarship.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Languages \& Certificates}
\resumeSubHeadingListStart
  \resumeSubheading
    {Languages}{}
    {Korean (Native), English (Fluent, C1), German (Fluent, C1), French (Basic, A2--B1)}{}

  \resumeSubheading
    {Selected Certificates}{}
    {Goethe Institute C1; OPIc English IH; Coursera coursework in marketing, branding, and positive psychology}{}
\resumeSubHeadingListEnd

\end{document}
